### 2015-11-05 CVPR16/Source/applications.tex
Reorganize Section 4

\subsection{Object-Point Association}
Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ of the $j$\textsuperscript{th} point track with $i$\textsuperscript{th} object at depth $\lambda$ can be defined as
\begin{align}
  \assocP = \Prefl\Ptrans,
\end{align}
where $\Prefl$ and $\Ptrans$ are from \eqref{eq:evalPrefl} and \eqref{eq:evalCumulativePtrans} respectively. Note that the fraction $\assocP$ although called association probability does not capture the entire information that we have available for computing association of point tracks to objects. This above fraction is the association probability given the hypothesized parameters of objects in the scene.

@@

\subsubsection{Continuous point tracks energy with occlusion}
\label{sec:totalContPtTracksEnergy}
We model continuous point tracks energy with explicit occlusion reasoning as
the expected reprojection error over the association probability,

\begin{multline}
  \Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \\
    \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
\end{multline}
where $\assocP$ is the association probability of
$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$, $\{ \relp{i}{t} \}_i$ are the poses of all occluding objects at time $t$, $ \{ \dimsn{i} \}_i$ are the dimensions of all objects that occlude $i$
and $\Ereproj(\lambda)$ is the reprojection error given by
%
\begin{align}
  \assocP &= \Prefl\Ptrans\\
  \Ereproj(\lambda) &= \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2 .
  \label{eq:reprojerror}
\end{align}

The  $\projectionOf{.}$ and $\invProjectionOftm{.}$ denote the projection and
inverse projection functions that project 3D point to camera image and vice
versa. Note that inverse projection $\invProjectionOf{.}$ depend on both the
point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t-1$ while the projection depends on pose at time $t$ which can be different.

>>>>

\subsection{Object-Point Association}
Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ of the $j$\textsuperscript{th} point track with $i$\textsuperscript{th} object at depth $\lambda$ can be defined as
\begin{align}
\assocP = \Prefl\Ptrans,
\label{eq:defineassocP}
\end{align}
where $\Prefl$ and $\Ptrans$ are from \eqref{eq:evalPrefl} and \eqref{eq:evalCumulativePtrans} respectively. Note that the fraction $\assocP$ although called association probability does not capture the entire information that we have available for computing association of point tracks to objects. This above fraction is the association probability given the hypothesized parameters of objects in the scene.

@@

\subsubsection{Continuous point tracks energy with occlusion}
\label{sec:totalContPtTracksEnergy}

Let the pose of object $i$ at time $t$ be $\relp{i}{t}$. We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ for the projection and inverse projection functions that project a 3D point to the camera image and vice versa. Then, the reprojection error for the $j$\textsuperscript{th} 2D point, with hypothesized depth $\lambda$, is given by
\begin{equation}
\Ereproj(\lambda) = \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2.
\label{eq:reprojerror}
\end{equation}
Note that inverse projection $\invProjectionOf{.}$ depends on both the 2D point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on object pose at time $t-1$ while the forward projection depends on pose at time $t$ which can be different.

For an object $i$, let $\{ \relp{i}{t} \}_i$ be the poses of all occluding objects at time $t$ and $ \{ \dimsn{i} \}_i$ be their dimensions. Then, we model the continuous point tracks energy with explicit occlusion reasoning as the expected reprojection error over the association probability:
\begin{multline}
  \Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \\
    \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
\end{multline}
where $\assocP$ is the association probability of the $j$\textsuperscript{th} point with the $i$\textsuperscript{th} object at depth $\lambda$, given by \eqref{eq:defineassocP}.

%\begin{align}
%  \assocP &= \Prefl\Ptrans\\
%  \Ereproj(\lambda) &= \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2 .
%  \label{eq:reprojerror}
%\end{align}

%The $\projectionOf{.}$ and $\invProjectionOftm{.}$ denote the projection and inverse projection functions that project 3D point to camera image and vice versa. Note that inverse projection $\invProjectionOf{.}$ depend on both the point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t-1$ while the projection depends on pose at time $t$ which can be different.
